Test

### 2016-07-22 Berkeley_PD_Stop.Rmd
update

#mutate dispositions column to only contain six character cases

View(stop_df)
View(dispositions)
###

>>>>

#mutate dispositions column to only contain six character cases
stop_df <- mutate(stop_df, Dispositions = str_match_all(stop_df$Dispositions, "[a-zA-Z0-9]{6}"))

dispositions <- separate(stop_df, Dispositions, into = c("Empty", "Individual_1", "Individual_2", "Individual_3", "Individual_4", "Individual_5"), extra = "merge", fill = "right")

View(stop_df)
View(dispositions)

###IGNORE EVERYTHING AFTER THIS
